Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 schemes.tex
Detailing SRLNC

In \ac{SRLNC}, instead of considering all the packets to create a coded
packet as in \ac{RLNC}, for this coding scheme an encoder sets more
coding coefficients to zero when generating a coded packet. A way to
accomplish this, is to set a fixed ratio of non-zero coefficients
in the encoding vector of size $g$. We refer to this fixed ratio as the
average coding density $d$. Thus, for any coded packet $C_i$ with coding
coefficients $v_{ij},\ j \in [1,g]$, its coding density is defined as follows:
%
\begin{align}
\label{eq:coding_density}
d = \frac{\sum_{j=1}^{g} f(v_{ij})}{g},\ \
    f(v_{ij}) =
    \begin{cases}
        0 & \text{for } v_{ij} = 0 \\
        1 & \text{for } v_{ij} \neq 0
    \end{cases}
\end{align}
%
From the density definition in \eqref{eq:coding_density}, it can be
observed that $0 \leq d \leq 1$. As $g$ increased, we obtain more
granularity in the density. Notice that the special case $d = 0$ has no
practical purpose since it implies just zero padded data. So, a practical
range for the density excludes the zero case, $0 < d \leq 1$. Moreover,
it can be also observed that the case of $d = 1$ reduces to the \ac{RLNC}
coding scheme described in Section \ref{ssec:RLNC}.

@@

The drawback of this scheme is that coded packets from the encoder
become more \ac{l.d.} on each other as the density is reduced.
This leads to transmission overhead since another coded packet
is required to be sent for every reception of a redundant packet.
Also, particularly with this method, generating a coded packet may imply
that it could not contain any data at all. For example, we might find
the case where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] =
\mathbf{0}$. In that case, the encoder discards the coded packet
and tries to generate a new one. This situation occurs more frequently
as the density is reduced.

Under the current method for setting the density, most coded packets that
are produced by the encoder are typically very sparse.
The reason being that here we control the \textit{average} amount
of nonzero coefficients, but not the exact value for each coded packet. Therefore,
we may have some cases where we have more or less packets combined. A second
implementation in Kodo considers doing something more clever.

>>>>

In \ac{SRLNC}, instead of considering all the packets to create a coded
packet as in \ac{RLNC}, for this coding scheme an encoder sets more
coding coefficients to zero when generating a coded packet with the purpose
of reducing the overall processing in both encoding and decoding. In what
follows, we describe the coding scheme with a basic method to produce sparse
coded packets and later we indicate a second one, giving reference to their
implementation performance.

\subsubsection{Method 1: Fixing the Coding Density}
A way to control the amount of non-zero coding coefficients, is to set a
fixed ratio of non-zero coefficients in the encoding vector of size $g$. We
refer to this fixed ratio as the average coding density $d$. Thus, for any
coded packet $C_i$ with coding coefficients $v_{ij},\ j \in [1,g]$, its
coding density is defined as follows:
%
\begin{align}
\label{eq:coding_density}
d = \frac{\sum_{j=1}^{g} f(v_{ij})}{g},\ \
    f(v_{ij}) =
    \begin{cases}
        0 & \text{for } v_{ij} = 0 \\
        1 & \text{for } v_{ij} \neq 0
    \end{cases}
\end{align}
%
From the density definition in \eqref{eq:coding_density}, it can be
observed that $0 \leq d \leq 1$. As $g$ increased, we obtain more
granularity in the density. Notice that the special case $d = 0$ has no
practical purpose since it implies just zero padded data. So, a practical
range for the density excludes the zero case, $0 < d \leq 1$. Moreover,
it can be also observed that the case of $d = 1$ reduces to the \ac{RLNC}
coding scheme described in Section \ref{ssec:RLNC}.

@@

The drawback of this scheme is that coded packets from the encoder
become more \ac{l.d.} on each other as the density is reduced.
This leads to transmission overhead since another coded packet
is required to be sent for every reception of a redundant packet.
Also, particularly with this method, we may still generate a coded packet
which does not contain any data at all. For example, we might find
the case where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] =
\mathbf{0}$. In that case, the encoder discards the coded packet
and tries to generate a new one. This situation occurs more frequently
as the density is reduced.

\subsubsection{Method 2: Sampling the Amount of Packets to Combine}
The method described from \eqref{eq:sparse_coded_packet} permits
to obtain a fast implementation in terms of execution time for
$d \geq 0.3$ \textbf{Include reference here}. Nevertheless, for $d < 0.3$
the implementation becomes slow given that more Bernoulli trials are
required in total for all random variables to generate a coded packet.
Thus, we introduce a second method that permits a fast implementation
for low coding densities  \textbf{Same reference here}.

For this method, we first calculate the amount of coding coefficients
that we will use to combine.

The second method
% The reason being that here we control the \textit{average} amount
% of nonzero coefficients, but not the exact value for each coded packet. Therefore,
% we may have some cases where we have more or less packets combined. A second
% implementation in Kodo considers doing something more clever.
